Making multiple-locus association mapping on a genome-wide scale routine

### 2017-09-27 AM+draft.tex
270917 Finished first draft of Methods - Overview - happy with this.

\subsection{Our Multiple-Locus Association Mapping Approach}
\subsubsection{Overview}

Eagle is an approach that identifies genomic regions of interest for a trait via the building of a (linear mixed) model. The model is built iteratively, without need of significance levels or thresholds. The model has two parts, a fixed effects part and a random effects part. The random effects 
part models the error and association across the entire genome. It is from the random part that we are able to identify 
the snp in strongest association with the trait.  We then move this snp out from the random effects part of the model and 
into the fixed effects part.  This serves two purposes. First, by moving the snp into the fixed effects part of the model, we are accounting
 for its effect and the effect of its neighbours in the random part of the model. So, when we come an look for the next snp in association 
 with the trait, we do not find the neighbour of a snp already identified. Second, it allows us to discover snp-trait associations that would 
 otherwise be masked.  Our iterative process is to fit the model to the data,  identify the snp in strongest association with the trait from the 
 random effects part, move the snp into the fixed effects part and remove it from the random effects part, fit the new model, calculate if the new 
 model is a "better" fit to the data.  If so, continue the process.  The snps that have been moved into the fixed effects part are the findings from the 
 Eagle approach. Each snp identifies a separate region of the genome that houses genes that are influencing the trait. 
 Below, we present the details of the Eagle algorithm.

>>>>

\subsection{Eagle Approach for Multiple-locus Association Mapping}
\subsubsection{Overview}

Eagle is an approach that identifies genomic regions of interest for a trait via the building of a (linear mixed) model. The model is built iteratively, without need of significance levels or thresholds. The model has two parts, a fixed effects part and a random effects part. The random effects part contains the error and an effect for the snp-trait association across the entire genome. It is from this effect 
 that we are able to identify which snp is in strongest association with the trait.  
 Our model building process is as follows. First we fit the current model to the data. Second, from the random effect for association, we identify which snp is in strongest association  with the trait.  Third, we move this snp from the random effects to the fixed effects.
We do this to stop the neighbours of the chosen snp from being selected in subsequent iterations and 
to give opportunity to snp in linkage disequilibrium with genes having lesser impact on the trait to be discovered. 
 Fourth, we fit the  new model. Fifth, we calculate if the new model fits the data "better" than the current model.  If the new model is a better fit,  then we repeat the process.   Once the model building process is complete, the findings from Eagle are the set of snp that have been moved into the fixed effects part of the model.  These snp map the seperate regions of the genome that house genes that are influencing the trait.
